Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-10-05 LaTeX_paper/paper.tex
correct paper to section 5.1

\section{The Objective Of This Paper}\label{document:objective}
After reading some of the previous literature on this problem, some conclusions could be drawn:
The problem of digital jigsaw puzzle has been solved many times, and is already well optimized.\newline
On the other hand, the problem of real-world jigsaw puzzle has mostly been ignored
by the academic community.\newline
The first objective for this paper is to fill this void, and been the first formal paper to analyze the
real-world jigsaw puzzle problem.\newline
The second objective is to use the research that will be conducted for this paper to create a labeling tool.\newline
The reason behind this objective is that the biggest challenge for real world puzzles is creating a
reliable comparator~\ref{document:comparator}, that could provide accurate information even with noisy 
input data, that are obtained from real-world measure.\newline
It is easy to see how a machine learning based comparator would probably be the best solution, 
but this has some problems, in fact having to manually scan and label thousands of individual puzzle
pieces to train the model would take ages.
Instead an automatic tool would allow to scan a small $4\times4$ puzzle in one shot,
solve it, and return the labeled data in just minutes.

@@

To fulfill the objective of this paper some data to work with are needed.
This section will cover the input data used as well as the Splitter~\ref{document:splitter}
and Comparator~\ref{document:comparator} algorithms.

@@

The first step is finding a real world puzzle to solve;
It has been decided to use a classic 1000 piece 66cm x 50cm  puzzle, and use a printer's
scanner to digitize the pieces.\newline 
The puzzle has been scanned in various sub-sizes to allow the testing of different configurations. 
A resolution of 1200 ppi has been used to ensure a sharp and precise image
of the piece, as seen in image~\ref{fig:figure_measurement_error}.
The puzzle has been scanned backward, using a black background.

This choice has been dictated by the fact that the scanner used has the flashlight
slightly off centered from the scanner's sensor.
And this causes a shadows to be cast on one side of the pieces.
A black background has been chosen to solve the problem of the shadow.
And then the pieces has been flipped backward, since many of them where black,
and it was difficult to separate them from the background.
In the future it would be possible to scan the pieces in the correct orientation,
by using a different scanner.

>>>>

\section{The Objective Of This Paper}\label{document:objective}
After a review of the existing literature on this problem, some conclusions could be drawn:
The "digital" jigsaw puzzle dilemma has been extensively addressed and is already
well-optimized. Conversely, the "real-world" counterpart has largely been
overlooked within the academic community.\newline
The first objective for this paper is to fill this void, and been the first formal paper
to analyze the real-world jigsaw puzzle problem.\newline
The second objective is to use the forthcoming research to create a labeling tool.\newline
This objective is motivated by the fact that the biggest challenge for real world puzzles is creating a
reliable comparator~\ref{document:comparator}, that could provide accurate information even with noisy 
input images, that are obtained from real-world measure.\newline
It is easy to see how a machine learning based comparator would probably be the best solution, 
but this poses problems, in fact having to manually scan and label thousands of individual puzzle
pieces to train the model would take ages.
Instead an automatic tool would allow to scan a small $4\times4$ puzzle in one shot,
solve it, and return the labeled data in just minutes.

@@

To fulfill the objectives of this paper,
it is essential to have the necessary data for analysis.
This section will encompass the input data utilized,
as well as the Splitter~\ref{document:splitter}
and Comparator~\ref{document:comparator} algorithms.

@@

The first step involves selecting a real-world
puzzle for solving. It has been decided to utilize a
classic 1000-piece puzzle measuring 66cm x 50cm.
A printer's scanner is employed to digitize the individual pieces.\newline

The puzzle has been scanned in various sub-sizes to facilitate the testing of different configurations.
A resolution of 1200 pixels per inch (ppi) has been employed to ensure a sharp and precise
depiction of the pieces, as seen in image~\ref{fig:figure_measurement_error}.
The puzzle has been scanned backward, using a black background.

This choice has been dictated by the fact that the scanner used has the flashlight
slightly off-centered from the scanner's sensor.
And this causes a shadows to be cast on one side of the pieces.
A black background has been chosen to solve the problem of the shadow.
And then the pieces has been flipped backward, since many of them where black,
and it was difficult to separate them from the background.
In the future it would be possible to scan the pieces in the correct orientation,
by using a different scanner.
